\mythesistitleNOTSYNPOSIS \tnote[fyi]{Synopsis title is ``Generalization of Consecutive Ones Property of Binary Matrices''}

### 2012-02-24 src/030chap3.tex
All content done except acknowledgement. TBD: - spell check - unusual whitespaces, wandering floats

Combining the ideas of path labeling, hypergraph isomorphism and its
induced path labeling we now define {\em feasiblity} of a path
labeling in Definition~\ref{def:feasibletpl}.

@@

One of the problems solved in this thesis \FTPL characterizes
feasibile tree path labeling.

@@

For interval labeling, \cite{nsnrs09} shows that if it is an ICPIA \ie
pairwise intersection cardinalities are preserved, then $d$-way
intersection cardinalities are preseved for $2 < d < n$. Thus, in a
way, pairwise intersections ``capture'' feasibility of an interval
labeling. In the same vein, the following lemma indicates that
three-way intersection cardinality ``captures'' $d$-way intersection
cardinalities for $3 < d < n$ in a tree path labeling.

@@

@@

  \caption[\figtabsize Problem solution part 1]{\figtabsize The
    problem is shown again here using the input described in
    Section~\ref{sec:problem}. The target tree is $T$ with vertex set
    $\{1,2,\ldots,11\}$ on the left hand side along with the path
    system (hypergraph) -- $\{7,2,6,5\}, \{8,2,4\}, \{10,6,5,3\},
    \{9,1,5,3,11\}$. The hypergraph is $\cF$ with hyperedges $\{\xPa,
    \xPi, \xVi, \xCh\}, \{\xSn, \xWo, \xPi\}, \{\xCh, \xFr, \xVi,
    \xLi\}, \{\xLu, \xSa, \xSc, \xCh, \xFr\}$ shown in the right hand
    side. In subsequent illustrations, the gray boxes which contain
    the elements of universe $U$, will be assigned to nodes and
    removed from the right hand side figure and placed next to the
    vertex of $T$ in the left hand side figure.  The path labeling is
    implicitly given by the color-coded Venn diagrams (the order of
    listing of the hyperedges in this caption is also done respective
    to the input path labeling).}
  \label{fig:solpartI}  
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    \infiniteloopIII 
    & 
    \studygroupsIII 
    &
    \studygroupsIIItable
  \end{tabular}
  \caption[\figtabsize Problem solution part 2]{\figtabsize It can be observed in
    Figure~\ref{fig:solpartI}, that none of the leaves are shared by
    more than one path. Hence, \filteri does not alter the
    hypergraphs. \filterii finds the leaf assignments as shown --
    elements \xPa, \xSn, \xLu, \xSc, \xLi, \xWo are assigned to
    vertices 7, 8, 9, 11, 10, 4 respectively. Computation of these
    leaf labels are deterministic except for $\xLu, \xSc$ where the
    algorithm arbritarily choses them from $X = \{\xLu, \xSa, \xSc\}$
    and for $\xSn, \xWo$ arbitrarily choses from $X = \{\xSn,
    \xWo\}$. Here we show only one such choice and clearly one could
    have chosen another leaf label (\eg $\xSa$ on 9 or $\xWo$ on 8) to
    get a different feasible hypergraph isomorphism.  After
    this, the leaves of $T$ are pruned and the hypergraph updated
    accordingly by \algoiii subroutine -- the pruned leaves are shown
    with dotted edges and the corresponding Venn diagrams show the
    updated hypergraphs. $\phi_0$ is this leaf assignment and the
    algorithm proceeds to solve the subproblem with the new
    hypergraphs and path labeling which is: $\{2,6,5\}, \{2\},
    \{6,5,3\}, \{1,5,3\}$ labeled with $\{\xPi, \xVi, \xCh\},
    \{\xPi\}, \{\xCh, \xFr, \xVi\}, \{\xSa, \xCh, \xFr\}$
    respectively.}
  \label{fig:solpartIII}  
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    \infiniteloopIVa
    & 
    \studygroupsIVa
  \end{tabular}
  \caption[\figtabsize Problem solution part 3]{\figtabsize In the subproblem shown in
    Figure~\ref{fig:solpartIII}, it can be noted that there are two
    leaves which are shared by more than one paths -- 2 and 3. Hence
    \filteri filters this out one by one. Here we show the handling of
    leaf 2 which was shared by paths $\{2,6,5\}$ ($=P_1$, say) and
    $\{2\}$($=P_2$, say). \filteri removes $P_1$ and adds
    $\{6,5\}$. Note that only one set is added and removed since $P_2
    \subset P_1$. Accordingly, \filteri alters the hypergraph on the
  right hand side by removing and adding $\{\xPi, \xVi, \xCh\}$ and $\{\xVi, \xCh\}$ respectively.}
  \label{fig:solpartIVa}  
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    \infiniteloopIVb
    & 
    \studygroupsIVb
  \end{tabular}
  \caption[\figtabsize Problem solution part 4]{\figtabsize After handling leaf 2, \filteri proceeds to
    handle leaf 3 which is shared by paths $\{1,5,3\}$ and
    $\{6,5,3\}$. \filteri removes these two paths and adds their
    intersection and set differences -- $\{5,3\}$, $\{1\}$ and
    $\{6\}$. Correspondingly, hyperedges $\{\xSa, \xCh, \xFr\}$ and $\{\xVi,
    \xCh, \xFr\}$ are removed and new hyperedges $\{\xCh, \xFr\}$, $\{\xSa\}$
    and $\{\xVi\}$ respectively are added. There are no more leaves
    shared and the algorithm proceeds to \filterii.}
  \label{fig:solpartIVb}  
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    \infiniteloopVI
    & 
    \studygroupsVI
    &
    \studygroupsVItable
  \end{tabular}
  \caption[\figtabsize Problem solution part 5]{\figtabsize \filterii computes the leaf assignment $\phi_1$ -- $\xPi,
    \xSa, \xFr$ on 2,1,3 respectively. These assignments are
    deterministic since $X$ consisted of only single elements for each
  of these leaves. After this the rest of the labeling is fairly
  obvious but we present it in Figure~\ref{fig:solpartVII} for the
  sake of completeness.}
  \label{fig:solpartVI}  
\end{figure}
\clearpage

@@

    \infiniteloopVII 
    &
    &
    \studygroupsVIItable
  \end{tabular}
  \caption[\figtabsize Problem solution part 6]{\figtabsize The last part of the isomorphism is computed as
  the leaf label $\phi_2$ which maps $\xCh, \xVi$ to 5, 6
  respectively. Figure~\ref{fig:solpartVIII} shows the final
  feasibility isomorphism which is the union of all the leaf labels.}
  \label{fig:solpartVII}  
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    \infiniteloopVIII
    &
    &
    \studygroupsVIIItable
  \end{tabular}
  \caption[\figtabsize Problem solution part 7]{\figtabsize The solution to the problem presented in
    Figure~\ref{fig:solpartI}. The feasibility hypergraph isomorphism
    $\phi$ is computed as the union of the leaf labels
    $\phi_0,\phi_1,\phi_2$. One can easily verify that this
    isomorphism does indeed induce the path labeling given in the
    original input.}
  \label{fig:solpartVIII}
\end{figure}

@@

In Section~\ref{sec:motive} it is described how \COP is a
special case of TPL as described by the \CFTPLINT problem. In this
section we will dwell on this in more detail.

\annote[dire]{The special case of TPL where the target tree $T$ is a
path. Hence, all path labels are can be viewed as intervals assigned
to the sets in $\cF$. }{needs work}

It is shown, in \cite{nsnrs09}, that the
filtering algorithms outlined above need only preserve pairwise
intersection cardinalities, and higher level intersection
cardinalities are preserved by the Helly Property of intervals.
% Consequently, the filter algorithms do not need to ever evaluate the
% additional check to {\em \bf exit}.
%\begin{enumerate}
%\item Given tree $T$ is a path. Hence, all path labels are interval labels.
%\item Only pairwise intersection cardinality
%  preservation is sufficient. i.e. property (iii) in ICPPL is not enforced.
%\item The filter algorithms do not have {\em \bf exit} statements.
%\end{enumerate}
%This is called an Intersection Cardinality Preservation Interval
%Assignment (ICPIA) \cite{nsnrs09}. 
This structure and its algorithm is used in the next section for
finding tree path labeling from a $k$-subdivided star due to this
graph's close relationship with intervals.

\tnote[dire]{ELABORATE}

@@

\tnote[dire]{REPEAT!!

In this section we consider the problem of assigning paths from a
$k$-subdivided star $T$ to a given set system $\cF$ such that each set
$X \in \cF$ is of cardinality at most $k+2$.  Secondly, we present our
results only for the case when overlap graph $\bO(\cF)$ is connected.
%The
%overlap graph is well-known from the work of
%\cite{kklv10,nsnrs09,wlh02}.  We use the notation in
%\cite{kklv10}. Recall from Section~\ref{sec:prelims} that hyperedges
%$S$ and $S'$ are said to overlap, denoted by $S \overlap S'$, if $S$ and $S'$
%have a non-empty intersection but neither of them is contained in the
%other. The overlap graph $\bO(\cF)$ is a graph in which the vertices
%correspond to the sets in $\cF$, and the vertices corresponding to the
%hyperedges $S$ and $S'$ are adjacent if and only if they overlap.  Note
%that the intersection graph of $\cF$, $\bI(\cF)$ is different from
%$\bO(\cF)$ and $\bO(\cF) \subseteq \bI(\cF)$.  
A connected component of $\bO(\cF)$ is called an overlap component of
$\cF$.  An interesting property of the overlap components is that any
two distinct overlap components, say $\cO_1$ and $\cO_2$, are such
that any two sets $S_1 \in \cO_1$ and $S_2 \in \cO_2$ are disjoint,
or, w.l.o.g, all the sets in $\cO_1$ are contained within one set in
$\cO_2$.  This containment relation naturally determines a
decomposition of the overlap components into rooted containment trees.
We consider the case when there is only one rooted containment tree,
and we first present our algorithm when $\bO(\cF)$ is connected.  It
is easy to see that once the path labeling to the overlap component in
the root of the containment tree is achieved, the path labeling to the
other overlap components in the rooted containment tree is essentially
finding a path labeling when the target tree is a path: each target
path is a path that is allocated to sets in the root overlap
component.  Therefore, for the rest of this section, $\bO(\cF)$ is a
connected graph. Recall that we also consider the special case when
all hyperedges are of cardinality at most $k+2$.  By definition, a
$k$-subdivided star has a central vertex which we call the {\em root},
and each root to leaf path is called a {\em ray}.  First, we observe
that by removing the root $r$ from $T$, we get a collection of $p$
vertex disjoint paths of length $k+1$, $p$ being the number of leaves
in $T$.  We denote the rays by $R_1, \ldots, R_p$, and the number of
vertices in $R_i$, $i \in [p]$ is $k+2$.  Let
$\seq{v_{i1},\ldots,v_{i(k+2)}=r}$ denote the sequence of vertices in
$R_i$, where $v_{i1}$ is the leaf. Note that $r$ is a common vertex to
all $R_i$.
}

@@

 \xnoindent The algorithm proceeds in iterations, and in the $i$-th
 iteration, $i > 1$, a single hyperedge $X$ that overlaps with a
 hyperedge that has been assigned a path is considered.  At the
 beginning of each iteration hyperedges of $\cO$ are classifed into
 the following disjoint sets.
 \begin{enumerate}
 \item [$\cL_1^i$] {\em Labeled without $r$.} Those that have been
   labeled with a path which does not contain $r$ in one of the
   previous iterations.\\  $\cL_1^i = \set{ X \mid p_1(X) = |X| \text{ and
     } p_2(X) = 0 \text{ and } s(X) = 0, X \in \cO}$
 \item [$\cL_2^i$] {\em Labeled with $r$.} Those that have been labeled
   with two subpaths of $\cl(X)$ containing $r$ from two different rays
   in two previous iterations.\\ $\cL_2^i = \set{X \mid 0 < p_1\left(X\right),
     p_2\left(X\right) < |X|=p_1(X)+p_2(X) \text{ and } s(X) = 0, X \in \cO}$
   \item [$\cT_1^i$] {\em Type 1 / partially labeled.} Those that have
     been labeled with one path containing $r$ from a single ray in one
     of the previous iterations. Here, $p_1(X)$ denotes the length of
     the subpath of $\cl(X)$ that $X$ has been so far labeled
     with. \\
     $\cT_1^i = \set{ X \mid 0 < p_1(X) < |X| \text{ and } p_2(X) = 0
       \text{ and } s(X) = |X|-p_1(X), X \in \cO}$
   \item [$\cT_2^i$] {\em Type 2 / not labeled.} Those that have not been
     labeled with a path in any previous iteration.\\
     $\cT_2^i = \set{ X \mid p_1(X) = p_2(X) = 0 \text{ and } s(X) = |X|,
       X \in \cO}$
 \end{enumerate}
% \vspace{-2mm}
% \begin{align*}
%   \cO &= \cL_1^i \cup \cL_2^i \cup \cT_1^i \cup \cT_2^i, \text{    } \forall i \in [p]\\
%   \cO_i &= \cT_1^i \cup \cT_2^i, \text{    } \forall i \in [p]
% \end{align*}

@@

\noindent
\begin{enumerate}[I.]
\item {\bf Iteration 1:} Let $S=\{X_1,\ldots,X_s\}$ denote the
  super-marginal hyperedges from $\cO_1$.  If $|S|=s \neq p$, then
  exit reporting failure.  Else, assign to each $X_j \in S$, the path
  from $R_j$ such that the path contains the leaf in $R_j$.  This path
  is refered to as $\cl(X_j)$.  Set $p_1(X_j)=|X|, p_2(X_j)=s(X_j)=0$.
  Hyperedges in $S$ are not added to $\cO_2$ but are added to
  $\cL_1^2$ and all other hyperedges are added to
  $\cO_2$.
\item {\bf Iteration $i$:} Let $X$ be a hyperedge from $\cO_i$ such
  that there exists $Y \in \cL_1^i \cup \cL_2^i$ and $X \overlap
  Y$. Further let $Z \in \cL_1^i \cup L_2^i$ such that $Z \overlap Y$.
  If $X \in \cT_2^i$, and if there are multiple $Y$ candidates then
  any $Y$ is selected.  On the other hand, if $X \in \cT_1^i$, then
  $X$ has a partial path assignment, $\cl'(X)$ from a previous
  iteration, say from ray $R_j$. Then, $Y$ is
  chosen such that $X \cap Y$ has a non-empty intersection with a ray
  different from $R_j$.  The key things that are done in assigning a
  path to $X$ are as follows. The {\em end} of path $\cl(Y)$ where
  $\cl(X)$ would overlap is found, and then based on this the
  existence of a feasible assignment is decided.  It is important to
  note that since $X \overlap Y$, $\cl(X) \overlap \cl(Y)$ in any
  feasible assignment.  Therefore, the notion of the {\em end} at
  which $\cl(X)$ and $\cl(Y)$ overlap is unambiguous, since for any
  path, there are two end points.
  \begin{enumerate}
  \item \label{iendpoint} {\em End point of $\cl(Y)$ where $\cl(X)$ overlaps
      depends on $X \cap Z$:} If $X \cap Z
    \neq \emptyset$, then $\cl(X)$ has an overlap of $|X \cap Y|$ at that
    end of $\cl(Y)$ at which $\cl(Y)$ and $\cl(Z)$ overlap.  If $X
    \cap Z = \emptyset$, then $\cl(X)$ has an overlap of $|X \cap Y|$ at
    that end of $\cl(Y)$ where $\cl(Y)$ and $\cl(Z)$ do not intersect.
  \item {\em Any path of length $s(X)$ at the appropriate end contains
      $r$:} If $X \in \cT_1^i$ then after finding the appropriate end
    as in step~\ref{iendpoint} this the unique path of length $s(X)$
    should end at $r$.  If not, we exit reporting failure.  Else,
    $\cl(X)$ is computed as union of $\cl'(X)$ and this path. If any
    three-way intersection cardinality is violated with this new
    assignment, then exit, reporting failure.  Otherwise, $X$ is added
    to $\cL_2^{i+1}$.  On the other hand, if $X \in \cT_2^i$, then
    after step~\ref{iendpoint}, $\cl(X)$ or $\cl'(X)$ is unique up to
    the root and including it. Clearly, the vertices $\cl(X)$ or
    $\cl'(X)$ contains depends on $|X|$ and $|X \cap Y|$.  If any
    three way intersection cardinality is violated due to this
    assignment, exit, reporting failure.  Otherwise,
    $p_1(X)$ is updated as the length of the assigned path, and $s(X)
    = |X|-p_1(X)$.  If $s(X) > 0$, then $X$ is added to $\cT_1^{i+1}$.
    If $s(X)=0$, then $X$ is added to $\cL_1^{i+1}$.
  \item {\em The unique path of length $s(X)$ overlapping at the
      appropriate end of $Y$ does not contain $r$:} In this case,
    $\cl(X)$ is updated to include this path.  If any three way
    intersection cardinality is violated, exit, reporting failure.
    Otherwise, update $p_1(X)$ and $p_2(X)$ are appropriate, $X$ is
    added to $\cL_1^{i+1}$ or $\cL_2^{i+1}$, as appropriate.
  \end{enumerate}
\end{enumerate}

>>>>

Combining the ideas of path labeling, hypergraph isomorphism and its
induced path labeling we now define {\em feasibility} of a path
labeling in Definition~\ref{def:feasibletpl}.

@@

One of the problems solved in this thesis \FTPL characterizes
feasible tree path labeling.

@@

For interval labeling, \cite{nsnrs09} shows that if it is an ICPIA \ie
pairwise intersection cardinalities are preserved, then $d$-way
intersection cardinalities are preserved for $2 < d < n$. Thus, in a
way, pairwise intersections ``capture'' feasibility of an interval
labeling. In the same vein, the following lemma indicates that
three-way intersection cardinality ``captures'' $d$-way intersection
cardinalities for $3 < d < n$ in a tree path labeling.

@@

In Figure~\ref{fig:solpartI}, the original problem from
Section~\ref{sec:problem} is restated more formally. The target tree
is $T$ with vertex set $\{1,2,\ldots,11\}$ on the left hand side along
with the path system (hypergraph) -- $\{7,2,6,5\}, \{8,2,4\},
\{10,6,5,3\}, \{9,1,5,3,11\}$. The hypergraph is $\cF$ with hyperedges
$\{\xPa, \xPi, \xVi, \xCh\}, \{\xSn, \xWo, \xPi\}, \{\xCh, \xFr, \xVi,
\xLi\}, \{\xLu, \xSa, \xSc, \xCh, \xFr\}$ shown in the right hand
side. In subsequent illustrations, the gray boxes which contain the
elements of universe $U$, will be assigned to nodes and removed from
the right hand side figure and placed next to the vertex of $T$ in the
left hand side figure.  The path labeling is implicitly given by the
color-coded Venn diagrams (the order of listing of the hyperedges in
given above is also done respective to the input path labeling).

@@

  \caption[\figtabsize Problem solution part 1]{\figtabsize The
    problem is shown again here using the input described in
    Section~\ref{sec:problem}.}
  \label{fig:solpartI}  
\end{figure}

Now see
Figure~\ref{fig:solpartIII} to see how the algorithm proceeds.
Before that it can be observed in Figure~\ref{fig:solpartI}, that none of the
leaves are shared by more than one path.  Hence,
\filteri does not alter the hypergraphs. \filterii finds the leaf
assignments as shown -- elements \xPa, \xSn, \xLu, \xSc, \xLi, \xWo
are assigned to vertices 7, 8, 9, 11, 10, 4 respectively. Computation
of these leaf labels are deterministic except for $\xLu, \xSc$ where
the algorithm arbitrarily chooses them from $X = \{\xLu, \xSa, \xSc\}$
and for $\xSn, \xWo$ arbitrarily chooses from $X = \{\xSn,
\xWo\}$. Here we show only one such choice and clearly one could have
chosen another leaf label (\eg $\xSa$ on 9 or $\xWo$ on 8) to get a
different feasible hypergraph isomorphism.  After this, the leaves of
$T$ are pruned and the hypergraph updated accordingly by \algoiii
subroutine -- the pruned leaves are shown with dotted edges and the
corresponding Venn diagrams show the updated hypergraphs. $\phi_0$ is
this leaf assignment and the algorithm proceeds to solve the
subproblem with the new hypergraphs and path labeling which is:
$\{2,6,5\}, \{2\}, \{6,5,3\}, \{1,5,3\}$ labeled with $\{\xPi, \xVi,
\xCh\}, \{\xPi\}, \{\xCh, \xFr, \xVi\}, \{\xSa, \xCh, \xFr\}$
respectively.

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    \infiniteloopIII 
    & 
    \studygroupsIII 
    &
    \studygroupsIIItable
  \end{tabular}
  \caption[\figtabsize Problem solution part 2]{\figtabsize \filterii
    finds leaf assignments as shown.}
  \label{fig:solpartIII}  
\end{figure}

In the subproblem shown in Figure~\ref{fig:solpartIII}, it can be
noted that there are two leaves which are shared by more than one
paths -- 2 and 3. Hence \filteri filters this out one by one. 
In Figure~\ref{fig:solpartIVa}, we
show the handling of leaf 2 which was shared by paths $\{2,6,5\}$
($=P_1$, say) and $\{2\}$($=P_2$, say). \filteri removes $P_1$ and
adds $\{6,5\}$. Note that only one set is added and removed since $P_2
\subset P_1$. Accordingly, \filteri alters the hypergraph on the right
hand side by removing and adding $\{\xPi, \xVi, \xCh\}$ and $\{\xVi,
\xCh\}$ respectively.

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    \infiniteloopIVa
    & 
    \studygroupsIVa
  \end{tabular}
  \caption[\figtabsize Problem solution part 3]{\figtabsize \filteri
    handling shared leaf 2.}
  \label{fig:solpartIVa}  
\end{figure}

After handling leaf 2, \filteri proceeds to handle leaf 3 which is
shared by paths $\{1,5,3\}$ and $\{6,5,3\}$. This is illustrated in
Figure~\ref{fig:solpartIVb}. \filteri removes these two paths and adds
their intersection and set differences -- $\{5,3\}$, $\{1\}$ and
$\{6\}$. Correspondingly, hyperedges $\{\xSa, \xCh, \xFr\}$ and
$\{\xVi, \xCh, \xFr\}$ are removed and new hyperedges $\{\xCh,
\xFr\}$, $\{\xSa\}$ and $\{\xVi\}$ respectively are added. There are
no more leaves shared and the algorithm proceeds to \filterii.

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    \infiniteloopIVb
    & 
    \studygroupsIVb
  \end{tabular}
  \caption[\figtabsize Problem solution part 4]{\figtabsize \filteri
    handles shared leaf 3.}
  \label{fig:solpartIVb}  
\end{figure}

Next, Figure~\ref{fig:solpartVI} shows how \filterii computes the leaf
assignment $\phi_1$ -- $\xPi, \xSa, \xFr$ on 2,1,3 respectively. These
assignments are deterministic since $X$ consisted of only single
elements for each of these leaves. After this the rest of the labeling
is fairly obvious but we present it in Figure~\ref{fig:solpartVII} for
the sake of completeness.

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    \infiniteloopVI
    & 
    \studygroupsVI
    &
    \studygroupsVItable
  \end{tabular}
  \caption[\figtabsize Problem solution part 5]{\figtabsize \filterii
    computes the leaf assignment $\phi_1$.}
  \label{fig:solpartVI}  
\end{figure}
%\clearpage

In Figure~\ref{fig:solpartVII}, the last part of the isomorphism is
computed as the leaf label $\phi_2$ which maps $\xCh, \xVi$ to 5, 6
respectively. Figure~\ref{fig:solpartVIII} shows the final feasibility
isomorphism which is the union of all the leaf labels. The feasibility
hypergraph isomorphism $\phi$ is computed as the union of the leaf
labels $\phi_0,\phi_1,\phi_2$. One can easily verify that this
isomorphism does indeed induce the path labeling given in the original
input.

@@

    \infiniteloopVII 
    &
    &
    \studygroupsVIItable
  \end{tabular}
  \caption[\figtabsize Problem solution part 6]{\figtabsize Last part
    of solution computed. }
  \label{fig:solpartVII}  
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tabular}[h]{c|cc}
    \infiniteloopVIII
    &
    &
    \studygroupsVIIItable
  \end{tabular}
  \caption[\figtabsize Problem solution part 7]{\figtabsize The solution to the problem presented in
    Figure~\ref{fig:solpartI}. }
  \label{fig:solpartVIII}
\end{figure}

@@

In Section~\ref{sec:motive} it is described how \COP is a special case
of TPL as described by the \CFTPLINT problem.  This special case of
TPL is where the target tree $T$ is a path. All path labels can now be
viewed as intervals assigned to the hyperedges in input hypergraph
$\cF$.  It is shown, in \cite{nsnrs09}, that the filtering algorithms
outlined above need only preserve pairwise intersection cardinalities,
and higher level intersection cardinalities are preserved by the Helly
Property of intervals. Thus ICPIA as described in
Section~\ref{sec:icpiasurvey} is a sufficient and necessary condition
for \COP and this is solvable in polynomial time.
% Consequently, the filter algorithms do not need to ever evaluate the
% additional check to {\em \bf exit}.
%\begin{enumerate}
%\item Given tree $T$ is a path. Hence, all path labels are interval labels.
%\item Only pairwise intersection cardinality
%  preservation is sufficient. i.e. property (iii) in ICPPL is not enforced.
%\item The filter algorithms do not have {\em \bf exit} statements.
%\end{enumerate}
%This is called an Intersection Cardinality Preservation Interval
%Assignment (ICPIA) \cite{nsnrs09}.

Moreover, this special case structure and its algorithm is used in the
next section for finding tree path labeling from a $k$-subdivided star
due to this tree's close relationship with intervals.

@@

% \tnote[dire]{REPEAT!!

% In this section we consider the problem of assigning paths from a
% $k$-subdivided star $T$ to a given set system $\cF$ such that each set
% $X \in \cF$ is of cardinality at most $k+2$.  Secondly, we present our
% results only for the case when overlap graph $\bO(\cF)$ is connected.

%The
%overlap graph is well-known from the work of
%\cite{kklv10,nsnrs09,wlh02}.  We use the notation in
%\cite{kklv10}. Recall from Section~\ref{sec:prelims} that hyperedges
%$S$ and $S'$ are said to overlap, denoted by $S \overlap S'$, if $S$ and $S'$
%have a non-empty intersection but neither of them is contained in the
%other. The overlap graph $\bO(\cF)$ is a graph in which the vertices
%correspond to the sets in $\cF$, and the vertices corresponding to the
%hyperedges $S$ and $S'$ are adjacent if and only if they overlap.  Note
%that the intersection graph of $\cF$, $\bI(\cF)$ is different from
%$\bO(\cF)$ and $\bO(\cF) \subseteq \bI(\cF)$.

% A connected component of $\bO(\cF)$ is called an overlap component of
% $\cF$.  An interesting property of the overlap components is that any
% two distinct overlap components, say $\cO_1$ and $\cO_2$, are such
% that any two sets $S_1 \in \cO_1$ and $S_2 \in \cO_2$ are disjoint,
% or, w.l.o.g, all the sets in $\cO_1$ are contained within one set in
% $\cO_2$.  This containment relation naturally determines a
% decomposition of the overlap components into rooted containment trees.
% We consider the case when there is only one rooted containment tree,
% and we first present our algorithm when $\bO(\cF)$ is connected.  It
% is easy to see that once the path labeling to the overlap component in
% the root of the containment tree is achieved, the path labeling to the
% other overlap components in the rooted containment tree is essentially
% finding a path labeling when the target tree is a path: each target
% path is a path that is allocated to sets in the root overlap
% component.  Therefore, for the rest of this section, $\bO(\cF)$ is a
% connected graph. Recall that we also consider the special case when
% all hyperedges are of cardinality at most $k+2$.  By definition, a
% $k$-subdivided star has a central vertex which we call the {\em root},
% and each root to leaf path is called a {\em ray}.  First, we observe
% that by removing the root $r$ from $T$, we get a collection of $p$
% vertex disjoint paths of length $k+1$, $p$ being the number of leaves
% in $T$.  We denote the rays by $R_1, \ldots, R_p$, and the number of
% vertices in $R_i$, $i \in [p]$ is $k+2$.  Let
% $\seq{v_{i1},\ldots,v_{i(k+2)}=r}$ denote the sequence of vertices in
% $R_i$, where $v_{i1}$ is the leaf. Note that $r$ is a common vertex to
% all $R_i$.
%}

@@

 \xnoindent The algorithm proceeds in iterations, and in the $i$-th
 iteration, $i > 1$, a single hyperedge $X$ that overlaps with a
 hyperedge that has been assigned a path is considered.  At the
 beginning of each iteration hyperedges of $\cO$ are classified into
 the following disjoint sets.
 \begin{enumerate}
 \item [$\cL_1^i$] {\em Labeled without $r$.} Those that have been
   labeled with a path which does not contain $r$ in one of the
   previous iterations.\\  $\cL_1^i = \set{ X \mid p_1(X) = |X| \text{ and
     } p_2(X) = 0 \text{ and } s(X) = 0, X \in \cO}$
 \item [$\cL_2^i$] {\em Labeled with $r$.} Those that have been labeled
   with two subpaths of $\cl(X)$ containing $r$ from two different rays
   in two previous iterations.\\ $\cL_2^i = \set{X \mid 0 < p_1\left(X\right),
     p_2\left(X\right) < |X|=p_1(X)+p_2(X) \text{ and } s(X) = 0, X \in \cO}$
   \item [$\cT_1^i$] {\em Type 1 / partially labeled.} Those that have
     been labeled with one path containing $r$ from a single ray in one
     of the previous iterations. Here, $p_1(X)$ denotes the length of
     the subpath of $\cl(X)$ that $X$ has been so far labeled
     with. \\
     $\cT_1^i = \set{ X \mid 0 < p_1(X) < |X| \text{ and } p_2(X) = 0
       \text{ and } s(X) = |X|-p_1(X), X \in \cO}$
   \item [$\cT_2^i$] {\em Type 2 / not labeled.} Those that have not been
     labeled with a path in any previous iteration.\\
     $\cT_2^i = \set{ X \mid p_1(X) = p_2(X) = 0 \text{ and } s(X) = |X|,
       X \in \cO}$
 \end{enumerate}
% \vspace{-2mm}
% \begin{align*}
%   \cO &= \cL_1^i \cup \cL_2^i \cup \cT_1^i \cup \cT_2^i, \text{    } \forall i \in [p]\\
%   \cO_i &= \cT_1^i \cup \cT_2^i, \text{    } \forall i \in [p]
% \end{align*}

@@

\noindent
\begin{enumerate}[I.]
\item {\bf Iteration 1:} Let $S=\{X_1,\ldots,X_s\}$ denote the
  super-marginal hyperedges from $\cO_1$.  If $|S|=s \neq p$, then
  exit reporting failure.  Else, assign to each $X_j \in S$, the path
  from $R_j$ such that the path contains the leaf in $R_j$.  This path
  is referred to as $\cl(X_j)$.  Set $p_1(X_j)=|X|, p_2(X_j)=s(X_j)=0$.
  Hyperedges in $S$ are not added to $\cO_2$ but are added to
  $\cL_1^2$ and all other hyperedges are added to
  $\cO_2$.
\item {\bf Iteration $i$:} Let $X$ be a hyperedge from $\cO_i$ such
  that there exists $Y \in \cL_1^i \cup \cL_2^i$ and $X \overlap
  Y$. Further let $Z \in \cL_1^i \cup L_2^i$ such that $Z \overlap Y$.
  If $X \in \cT_2^i$, and if there are multiple $Y$ candidates then
  any $Y$ is selected.  On the other hand, if $X \in \cT_1^i$, then
  $X$ has a partial path assignment, $\cl'(X)$ from a previous
  iteration, say from ray $R_j$. Then, $Y$ is
  chosen such that $X \cap Y$ has a non-empty intersection with a ray
  different from $R_j$.  The key things that are done in assigning a
  path to $X$ are as follows. The {\em end} of path $\cl(Y)$ where
  $\cl(X)$ would overlap is found, and then based on this the
  existence of a feasible assignment is decided.  It is important to
  note that since $X \overlap Y$, $\cl(X) \overlap \cl(Y)$ in any
  feasible assignment.  Therefore, the notion of the {\em end} at
  which $\cl(X)$ and $\cl(Y)$ overlap is unambiguous, since for any
  path, there are two end points.
  \begin{enumerate}
  \item \label{iendpoint} {\em End point of $\cl(Y)$ where $\cl(X)$ overlaps
      depends on $X \cap Z$:} If $X \cap Z
    \neq \emptyset$, then $\cl(X)$ has an overlap of $|X \cap Y|$ at that
    end of $\cl(Y)$ at which $\cl(Y)$ and $\cl(Z)$ overlap.  If $X
    \cap Z = \emptyset$, then $\cl(X)$ has an overlap of $|X \cap Y|$ at
    that end of $\cl(Y)$ where $\cl(Y)$ and $\cl(Z)$ do not intersect.
  \item {\em Any path of length $s(X)$ at the appropriate end contains
      $r$:} If $X \in \cT_1^i$ then after finding the appropriate end
    as in step~\ref{iendpoint} this the unique path of length $s(X)$
    should end at $r$.  If not, we exit reporting failure.  Else,
    $\cl(X)$ is computed as union of $\cl'(X)$ and this path. If any
    three-way intersection cardinality is violated with this new
    assignment, then exit, reporting failure.  Otherwise, $X$ is added
    to $\cL_2^{i+1}$.  On the other hand, if $X \in \cT_2^i$, then
    after step~\ref{iendpoint}, $\cl(X)$ or $\cl'(X)$ is unique up to
    the root and including it. Clearly, the vertices $\cl(X)$ or
    $\cl'(X)$ contains depends on $|X|$ and $|X \cap Y|$.  If any
    three way intersection cardinality is violated due to this
    assignment, exit, reporting failure.  Otherwise,
    $p_1(X)$ is updated as the length of the assigned path, and $s(X)
    = |X|-p_1(X)$.  If $s(X) > 0$, then $X$ is added to $\cT_1^{i+1}$.
    If $s(X)=0$, then $X$ is added to $\cL_1^{i+1}$.
  \item {\em The unique path of length $s(X)$ overlapping at the
      appropriate end of $Y$ does not contain $r$:} In this case,
    $\cl(X)$ is updated to include this path.  If any three way
    intersection cardinality is violated, exit, reporting failure.
    Otherwise, update $p_1(X)$ and $p_2(X)$ are appropriate, $X$ is
    added to $\cL_1^{i+1}$ or $\cL_2^{i+1}$, as appropriate.
  \end{enumerate}
\end{enumerate}
